Causal graph analysis of COVID-19 observational data in German districts reveals effects of determining factors on reported case numbers

### 2021-03-21 manuscript/v4_medrxiv_revision/results.Rmd
fix typo

The different intervention variables showed the strongest effects in our analysis, see Table \@ref(tab:causaleffects). While the first intervention (ban of mass gatherings) reduced subsequent daily case numbers by `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (ban of mass gatherings)")%>%pull("effect estimate")), 1)` percent, the closure of schools/kindergartens reduced infections by an additional `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (school and kindergarten closures)")%>%pull("effect estimate")), 1)` percent and mandatory face masks reduced this by another `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (mandatory face masks)")%>%pull("effect estimate")), 1)` percent. The effect of contatc restrictions was the strongest in our observation period, with an reduction of the case rates by `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (contact restrictions)")%>%pull("effect estimate")), 1)`.

>>>>

The different intervention variables showed the strongest effects in our analysis, see Table \@ref(tab:causaleffects). While the first intervention (ban of mass gatherings) reduced subsequent daily case numbers by `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (ban of mass gatherings)")%>%pull("effect estimate")), 1)` percent, the closure of schools/kindergartens reduced infections by an additional `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (school and kindergarten closures)")%>%pull("effect estimate")), 1)` percent and mandatory face masks reduced this by another `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (mandatory face masks)")%>%pull("effect estimate")), 1)` percent. The effect of contact restrictions was the strongest in our observation period, with an reduction of the case rates by `r round(100*abs(1-causaleffects%>%filter(cause=="Interventions (contact restrictions)")%>%pull("effect estimate")), 1)`.
